\onecolumn
%\section*{Bibliografia}
\biblio
\setlength{\parindent}{0pt}
\setlength{\parskip}{1ex plus 0.5ex minus 0.2ex}

Amer, Robin 2012. \bibtitle{How mah jongg became American (and Jewish)}.
\\https://www.wbez.org/shows/dynamic-range/how-mah-jongg-became-american-\\-and-jewish/ca81bfff-9276-48cb-b516-28ca218b36fe
[dostęp 2016-08-30].

Baum, Samuel 2009. \tytul{Lie to me}.

Babcock, Joseph P. [\&] Foster, R. F. [\&] Hartman, Lee F. [\&] Smith, John H.
[\&] Work, Milton C. 1924. ,,The American Code Of Laws For Mah-Jongg'' W:
\textit{Mah-Jongg Up-To-Date}. The John C. Winston Company. 
% brak stron imminent
%\\https://groups.google.com/forum/\#!msg/rec.games.mahjong/lTDLqLLykFY/g00IBFra\_skJ
% [dostęp 2016-08-01]

Benson, Raymond 1997. \bibtitle{Zero Minus Ten}. G.P. Putnam's Sons.

Carlisle, Rodney P. 2009. ,,Mahjong'' W: \textit{Encyclopedia of Play in Today's
Society}, 371-372.
Sage Publications.

Chang, Eileen 2007. \bibtitle{Lust, Caution}. Penguin Books Limited.

Christie, Agatha 2009. \bibtitle{Murder of Roger Ackroyd: A Hercules Poirot
Mystery}. Harper Collins.

Culin, Stewart 1924. ,,The Game of Ma-Jong'' W: \bibtitle{Brooklyn Museum
Quarterly}, Volume XI, 153-168.

Depaulis, Thierry [\&] Tsui, Cofa 2007. \bibtitle{Evolution of Various Forms of
Mahjong (1890-2001)}. 
\\http://www.imahjong.com/maiarchives205d\_3.html [dostęp
2016-08-01].

European Mahjong Association 2012. \bibtitle{\romaji{Riichi} -- Rules for
Japanese Mahjong}.
\\http://mahjong-europe.org/docs/riichi\_EN.pdf [dostęp 2016-08-05].

European Mahjong Association 2016. \bibtitle{\romaji{Riichi} -- Rules for
Japanese Mahjong}.
\\http://mahjong-europe.org/docs/Riichi-rules-2016-EN.pdf [dostęp 2016-08-05]

Greenfield, Mary C. 2010. „The Game of One Hundred Intelligences: ,,Mahjong,
Materials, and the Marketing of the Asian Exotic in the 1920s''. W:
\textit{Pacific Historical Review}, Vol. 79. 329-359.
% Carl Abott i David A. Johnson (ed.), \textit{Pacific Historical Review}, Vol.
% 79. 329-359. California: University of California Press.

Fisher, Linda 2016. \bibtitle{The Rules for Modern American Mah-jongg}.
\\https://sites.google.com/site/mahjrules/home/rules [dostęp 2016-08-30]

Harr, Lew Lysle 2008. \bibtitle{Pung Chow -- The Game of a Hundred
Intelligences.
Also known as Mah-Diao, Mah-Jong, Mah-Cheuk, Mah-Juck and Pe-Ling}. Project
Gutenberg.

Jīn Xuéshī 金学诗 1783. \bibtitle{Mùzhū Xiánhuà 牧猪闲话} [Plotki o Świniopasach].
Zhāodài Cóngshū 昭代丛书.

Kanazawa Masahiro 金澤正浩 2010. \romaji{,,2002 Sekaimājansenshuken taikai ni
tsuite''} 《2002 世界麻雀選手権大会について》 ([O Światowych Mistrzostwach
Świata w Madżongu 2002]).
\\http://www1.tcue.ac.jp/home1/takamatsu/100124/100124-002.pdf [dostęp
2016-04-25].

Knauf, Daniel 2003. \bibtitle{Carnivàle}. HBO.

Kolenda, Dominik 2012. \bibtitle{Mahjong w japońskiej kulturze popularnej --
Historia: Japonia}. Polska Liga Mahjonga.
\\https://mahjong.waw.pl/index.php?option=com\_content\&view=article\&id=11\&Itemid=128
[dostęp 2016-08-06].

\pinyin{Kǒuzhuāng Bāshì} 口装巴士 2014. \pinyin{,,Huānlè májiàng
yánshēn zhī shìjiè májiàng bǐsài jièshào''} 《乐麻将延伸之世界麻将比赛介绍》
[Popularyzacja madżonga poprzez wprowadzenie światowych zawodów
sportowych] \\http://m.ptbus.com/huanlemajiang/221298/ [dostęp 2016-04-25].

Lǐ, Ān (李安) 2007. \bibtitle{Sè, Jiè}\tytul 《色，戒》 [Ostrożnie, pożądanie].

Liú, Zhènwěi (劉鎮偉) 1996. \bibtitle{Maa4zoek3 Fei1lung4} 《麻雀飛龍》 [Mahjong Dragon].

Lo, Amy 2001. \bibtitle{The Book of Mah jong: An Illustrated Guide}. Tuttle
Publishing.

Mah Jong Museum. \bibtitle{Mah Jong Historical Documents}
\\http://www.mahjongmuseum.com/history.htm [dostęp
2016-03-30].

Maruyama, Masao (丸山正雄) 2005. \romaji{Akagi:} \romaji{Yami} \romaji{ni}
\romaji{Oritatta} \romaji{Tensai} 《アカギ闇に降り立った天才》 [Akagi: Geniusz, który zstąpił w
ciemność].

Miller, Scott D. 2013. \bibtitle{Mahjong From A To Zhú}. Psionic Press.

Miller, Scott D. 2015. \bibtitle{Riichi Mahjong: The Ultimate Guide to the
Japanese Game Taking the World By Storm}. Psionic Press.

National Mah Jongg League 2011. \bibtitle{The League}.
\\https://www.nationalmahjonggleague.org/league.html [dostęp 2016-08-30].

National Mah Jongg League 2016. \bibtitle{How to}.
\\https://www.nmjl.org/game/howto.html [dostęp 2016-08-30].

\romaji{Nihon kenkō asa shō kyōkai kōshiki saito} 日本健康麻将協会公式サイト  2002.
\\\romaji{2002 nen Sekaimājansenshuken Taikai Kojin Bumon Seiseki} 2002
年世界麻雀選手権大会個人部門成績 [Wyniki Indywidualne Światowych Zawodów Madżonga 2002]
\\http://www.kenko-mahjong.com/topics/sekaikojin.htm [dostęp 2016-04-25].

Polska Liga Mahjonga 2016. \bibtitle{Terminologia}
\\
https://mahjong.waw.pl/index.php?option=com\_content\&view=article\&id=24\&Itemid=147
[dostęp 2016-07-12].

Polska Liga Mahjonga 2016a. \bibtitle{Turnieje PLM -- System turniejowy Polskiej
Ligi Mahjonga} \\https://turnieje.mahjong.waw.pl/ [dostęp 2016-08-06].

Prattchett, Terry 2003. \bibtitle{Ciekawe Czasy}. Prószyński i S-ka.

Rep, Jelte 2006. \bibtitle{The Great Mahjong Book: History, Lore, and Play}.
Tuttle Publishing. %hkns 129-142

Sina \pinyin{Xīnlàng Lùntán} 新浪论坛 2010. \pinyin{Zhùmíng xuézhě Yú Guāngyuǎn,
wǎnnián wèishénme} \\\pinyin{qīngxīn hóngyáng májiàng wénhuà}
《著名学者于光远，晚年为什么倾心弘扬麻将文化》[Dlaczego szanowany uczony Yu Guangyuan na
starość całym sercem promuje kulturę gry w madżonga]
\\http://club.history.sina.com.cn/thread-4268500-1-1.html [dostęp 2016-06-27].

\pinyin{Shìjiè Májiàng Zǔzhī} 世界麻将组织 2014. \pinyin{Májiàng Jìngsài
Guīzé}《麻将竞赛规则》 [Światowe Zasady Madżonga]
\\http://www.chinamajiang.com/adobe\%20reader/z20140402.pdf [dostęp 2016-01-04].

Sloper, Tom [\&] inni autorzy 2006. \bibtitle{The CC Theory}
\\http://www.sloperama.com/cctheory/detail.html [dostęp
2016-03-30].

Sloper, Tom 2002. \bibtitle{Identifying a Mah-Jongg Variant}
\\http://www.sloperama.com/mjfaq/mjfaq02b.html [dostęp
2016-06-27].

Sloper, Tom 2006. \bibtitle{History of Mahjong}
\\http://www.sloperama.com/mjfaq/mjfaq11f.htm [dostęp 2016-08-01].

% TODO: rozróżnić a, b z różnych publikacji i tych samych lat
Stanwick, Michael 2004. ,,Mahjong(g) Before Mahjong(g): Part 1''. W:
\textit{The Playing-card}, Vol. 32, No. 4, 153-162.

Stanwick, Michael 2004a. ,,Mahjong(g) Before Mahjong(g): Part 2''. W:
\textit{The Playing-card}, Vol. 32, No. 5, 206-215.
% \\http://www.themahjongtileset.co.uk/tile-set-history/mahjongg-before-mahjongg-part-1/ 
% \\http://www.themahjongtileset.co.uk/tile-set-history/mahjongg-before-mahjongg-part-2/
% [dostęp
% 2016-03-30]

Stanwick, Michael 2006. ,,Mahjong(g) Before and After Mahjong(g): Part 1''. W:
\textit{The Playing-card}, Vol. 34, No. 4, 259-268.

Stanwick, Michael 2006a. ,,Mahjong(g) Before and After Mahjong(g): Part 2''. W:
\textit{The Playing-card}, Vol. 35, No. 1, 27-39.

% Stanwick, Michael 2006. \textit{Mahjong(g) Before And After Mahjong(g)}
% %\\http://www.themahjongtileset.co.uk/tile-set-history/mahjongg-before-and-after-mahjongg-part-1/
%  \\http://www.themahjongtileset.co.uk/tile-set-history/mahjongg-before-and-after-mahjongg-part-2/
% [dostęp
% 2016-03-30]

Stanwick, Michael [\&] Xu, Hongbing 2012. ,,From Cards to Tiles: The Origin of
\mbox{Mahjong(g)'s} Earliest Suit Names''. W:\textit{The Playing-card}, Vol. 41,
No.
1, 52–67.

Stanwick, Michael [\&] Xu, Hongbing. \bibtitle{Mahjong terms 1780 – 1920}
\\http://www.themahjongtileset.co.uk/mahjong-terms-1780-1920/ [dostęp
2016-03-30].

Tan, Amy 2006. \bibtitle{The Joy Luck Club}. Penguin.

Tse, Samson [\&] Yu, Alex C.H. [\&] Rossen, Fiona [\&] Wang, Chong-Wen
2010.
,,Examination of Chinese Gambling Problems through a Socio-Historical-Cultural Perspective''. W: \textit{The
Scientific World Journal}.

Walters, Ashley 2013. \bibtitle{From China to U.S., the game of mahjong shaped
modern America, says Stanford scholar}.
\\http://news.stanford.edu/news/2013/july/humanities-mahjong-history-071513.html
[dostęp 2016-08-30].

Wáng, Jīng (王晶) 2005. \bibtitle{Zoek3sing3} 《雀聖》 [Kung Fu Mahjong].

Wáng, Yǐng (王颖) 1993. \bibtitle{Xǐ Fú Huì} 《喜福会》 [The Joy Luck Club]. 

%Stanwick, Michael; Xu, Hongbing. \textit{From Cards to Tiles: The Origin of
% Mahjong(g)’s Earliest Suit Names}
%\\http://www.themahjongtileset.co.uk/tile-set-history/earliest-suit-names/
Wikipedia 2013. \bibtitle{George B. Glover}
\\https://en.wikipedia.org/wiki/George\_B.\_Glover [dostęp 2016-04-22].

Wikipedia 2016. \bibtitle{Stewart Culin}
\\https://en.wikipedia.org/wiki/Stewart\_Culin [dostęp 2016-04-22].

Wikipedia 2016a. \bibtitle{Yú Guāngyuǎn} 于光远
\\https://zh.wikipedia.org/wiki/\%E4\%BA\%8E\%E5\%85\%89\%E9\%81\%A0 [dostęp
2016-06-27].

% Work, Milton C. 1924. \textit{Mah-Jongg Up-To-Date}. The John C. Winston
% Company.

World Heritage Encyclopedia 2014. \bibtitle{Mahjong}
\\http://www.worldheritage.org/article/WHEBN0000019496/Mahjong [dostęp
2016-03-31].

World Series of Mahjong 2015. \bibtitle{Mahjong Around the World}
\\http://worldmahjong.com/about-mahjong/mahjong-around-the-world/ [dostęp
2016-06-27].

Zǐ Mò 梓沫 2015. \bibtitle{,,Cáipàn jiědú guóbiāo májiàng: Bā
fān qǐ ‘hé’ jiàngdī yùnqì chéngfèn''}《裁判解读国标麻将：八番起‘胡’降低运气成分》
[Interpretacja sędziego krajowego madżonga:
\pinyin{hu} przy 8 \pinyin{fan} zmniejsza szczęście] % tutaj jest o nowych
% zasadach z 1998
\\http://sports.sina.com.cn/go/2015-10-25/doc-ifxizwsi5588602.shtml [dostęp 2016-04-25].















